Will it blend: Is the Milky Way bar causing chaotic fanning of the Ophiuchus stream?

### 2015-08-14 ms.tex
paper outline

@@

\section{Potential model}\label{sec:potential}

@@

@@

\acknowledgements
APW is supported by a National Science Foundation Graduate Research Fellowship under Grant No.\ 11-44155.
This work was supported in part by the National Science Foundation under Grant No. PHYS-1066293.
This research made use of Astropy, a community-developed core Python package for Astronomy \citep{astropy13}.
This work additionally relied on Columbia University's \emph{Hotfoot} and \emph{Yeti} compute clusters, and we acknowledge the Columbia HPC support staff for assistance. \\

>>>>

The Ophiuchus stream \citep{bernard14} is located in an interesting region of the Milky Way. Many streams have been found in the halo at Galactocentric distances of XX--YY kpc, but Ophiuchus is situated near the Galactic center where the gravitational potential should have significant components from the bulge and bar of the Milky Way. Recent modeling fit for the orbit, found discrepancy between dynamical age and age of stellar populations \citep{sesar15}, however they assume an axisymmetric disk plus spherical bulge and halo. If the Galactic bar contributes significantly to the density distribution of the inner Galaxy, the orbit of the cluster could be entirely different.

@@

\subsection{Potential model}\label{sec:potential}

@@

\subsection{Mock streams}\label{sec:mocks}

\section{Results}

\subsection{The degree of chaos}\label{sec:results1}

\subsection{Reproducing the observed properties of the stream}\label{sec:results2}

@@

\acknowledgements
APW is supported by a National Science Foundation Graduate Research Fellowship under Grant No.\ 11-44155.
APW acknowledges the ... MPIA ...
This research made use of Astropy, a community-developed core Python package for Astronomy \citep{astropy13}.
This work additionally relied on Columbia University's \emph{Yeti} compute cluster, and we acknowledge the Columbia HPC support staff for assistance. \\
